---
title: "Brain_connectivity"
author: "Yiming Qian"
date: "2025-04-18"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(tidyverse)
library(ggplot2)
library(purrr)
library(broom.mixed) 
library(knitr)
library(kableExtra)
```


```{r}
df<- read.csv("C:/Users/ymqian/Documents/multimodal_amygdala/analysis/processed_data.csv")
```

rsfMRI: iqc_rsfmri_ok_ser>0, fsqc_qc=1 (Passed FreeSurfer QC), rsfmri_c_ngd_ntpoints > 375 (exclude excession motion) imgincl_rsfmri_include = 1 (I forget to ask for this variable)
controlling for mean framewise displacement
for all scans passing QC (iqc_rsfmri_ok_mean_motion) and number of frames after excluding
outlier frames (rsfmri_ntpoints),

```{r}
df_rsfMRI<- df  %>%  filter(iqc_t1_ok_ser > 0)  %>% filter(fsqc_qc != "reject" | is.na(fsqc_qc)) %>% filter(rsfmri_ntpoints> 750) 
```
from N= 11634 to N=7345

```{r}
amy_pds_fc<-lm(amygdala_fc~stage_p*demo_sex_v2, data=df_rsfMRI, na.action = na.omit)
anova(amy_pds_fc)
```

```{r}
amy_dhea_fc<-lm(amygdala_fc~dhea_corrected*demo_sex_v2, data=df_rsfMRI, na.action = na.omit)
anova(amy_dhea_fc)
```
```{r}
amy_test_fc<-lm(amygdala_fc~test_corrected*demo_sex_v2, data=df_rsfMRI, na.action = na.omit)
anova(amy_test_fc)
```
```{r}
amy_estr_fc<-lm(amygdala_fc~estr_corrected, data=df_rsfMRI, na.action = na.omit)
anova(amy_estr_fc)
```
other 
```{r}
dv_list <- c("amygdala_fc","amygdala_fc_df","amygdala_fc_cerc","amygdala_fc_vs","amygdala_fc_au","amygdala_fc_copa","amygdala_fc_dsa","amygdala_fc_fopa","amygdala_fc_none","amygdala_fc_rst","amygdala_fc_smh","amygdala_fc_smm","amygdala_fc_vta")
models <- map(dv_list, ~ lm(as.formula(paste(.x, "~ stage_p*demo_sex_v2")), 
                            data = df_rsfMRI, na.action = na.omit))

names(models) <- dv_list

# Example: get tidy results for all models
results <- map_df(models, tidy, .id = "DV")
pvals <- map_df(models, ~ tidy(.x) %>% 
                  select(term, estimate, p.value), 
                .id = "DV")
pvals <- pvals %>%
  mutate(p.value = round(p.value, 3),
         estimate = round(estimate, 3))
print(pvals)
```
whole brain, df, cerc,au, copa,dsa,fopa, none,rst,smh,smm,vta ~pubertal stage
whole brain, copa,fopa,vta ~sex
smh ~interaction
```{r}
models_dhea <- map(dv_list, ~ lm(as.formula(paste(.x, "~ dhea_corrected*demo_sex_v2")), 
                            data = df_rsfMRI, na.action = na.omit))

names(models_dhea) <- dv_list
pvals_dhea <- map_df(models_dhea, ~ tidy(.x) %>% 
                  select(term, estimate, p.value), 
                .id = "DV")
pvals_dhea <- pvals_dhea %>%
  mutate(p.value = round(p.value, 3),
         estimate = round(estimate, 3))
print(pvals_dhea)
```

whole brain,df,cerc,dsa,fopa,smh,smm ~dhea
whole brain,copa,dsa,fopa, smh,smm,vta ~sex
smh ~dhea*sex

```{r}
models_test <- map(dv_list, ~ lm(as.formula(paste(.x, "~ test_corrected*demo_sex_v2")), 
                            data = df_rsfMRI, na.action = na.omit))

names(models_test) <- dv_list
pvals_test<- map_df(models_test, ~ tidy(.x) %>% 
                  select(term, estimate, p.value), 
                .id = "DV")
pvals_test <- pvals_test %>%
  mutate(p.value = round(p.value, 3),
         estimate = round(estimate, 3))
print(pvals_test)
```
whole brain, df, cerc,fopa, smh, smm ~ test
whole brain, copa, dsa, fopa, smh, smm, vta ~sex

```{r}
models_estr <- map(dv_list, ~ lm(as.formula(paste(.x, "~ estr_corrected")), 
                            data = df_rsfMRI, na.action = na.omit))

names(models_estr) <- dv_list
pvals_estr <- map_df(models_estr, ~ tidy(.x) %>% 
                  select(term, estimate, p.value), 
                .id = "DV")
pvals_estr <- pvals_estr %>%
  mutate(p.value = round(p.value, 3),
         estimate = round(estimate, 3))
print(pvals_estr)
```
whole brain, cerc,dsa ~ estr

# sensirivity analysis (add cov)
```{r} 
models_dhea1<- map(dv_list, ~ {
  formula <- as.formula(paste(.x, "~ dhea_corrected * demo_sex_v2 + age + race_ethnicity + household.income + married2 + high.educ + pea_wiscv_trs + rsfmri_ntpoints + (1|mri_info_deviceserialnumber) + (1|mri_info_deviceserialnumber:rel_family_id)"))
  lmer(formula, data = df_rsfMRI, na.action = na.omit)})


names(models_dhea1) <- dv_list

# Extract tidy results
results_dhea1 <- map_df(models_dhea1, ~ tidy(.x, effects = "fixed", conf.int = TRUE), .id = "DV")

car::Anova(models_dhea1[[1]])
tab_model(models_dhea1[[1]], show.ci = FALSE, show.re.var = TRUE, show.p = TRUE,
          dv.labels = "My Outcome Variable")
```